Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-23 paper/main.tex
add citation

Mechanical properties of rod-shaped bacteria have been studied in great detail
experimentally~\cite{Chatterjee1988,Takeuchi2005,IWAI2002}.
It was found that the MreB protein is the driving force in maintaining their distinct elongated
shape~\cite{Ursell2014}, which plays an important role in the dynamics of
growth~\cite{Billaudeau2017}, division~\cite{Harry2001} and their collective
behaviour~\cite{vanGestel2015}.
Furthermore, it has been discovered that the rod can be bent thus introducing temporary elastic or
permanent plastic deformations~\cite{Amir2014_2}.
Rod-shaped Bacteria are an interesting target system since their physical form provides more surface
information compared to other forms such as spherical cells.
In addition, parameters such as growth rates have been found to vary across multiple
cells~\cite{Koutsoumanis2013} which highlights the need to incorporate this heterogeneity on a
single-cell level.

>>>>

Mechanical properties of rod-shaped bacteria have been studied in great detail
experimentally~\cite{Chatterjee1988,Takeuchi2005,IWAI2002}.
It was found that the MreB protein is the driving force in maintaining their distinct elongated
shape~\cite{Ursell2014}, which plays an important role in the dynamics of
growth~\cite{Billaudeau2017}, division~\cite{Harry2001} and their collective
behaviour~\cite{vanGestel2015,Balagam2015}.
Furthermore, it has been discovered that the rod can be bent thus introducing temporary elastic or
permanent plastic deformations~\cite{Amir2014_2}.
Rod-shaped Bacteria are an interesting target system since their physical form provides more surface
information compared to other forms such as spherical cells.
In addition, parameters such as growth rates have been found to vary across multiple
cells~\cite{Koutsoumanis2013} which highlights the need to incorporate this heterogeneity on a
single-cell level.
